---
title: "PinealGland Sample Night_2 Seurat_2.2.0"
author: "Joseph Mays"
output:
  html_notebook: default
  html_document: default
  pdf_document: default
---

Dependencies loaded using SetupDependencies.R script.

Import Filtered Barcodes from CellRanger. Filter out cells with less than 800 genes and genes represented in less than 2 cells.
```{r Pineal2_Night2 Import, echo=TRUE, message=FALSE, warning=FALSE, results="hide"}
Pineal2_Night2.matrix <- Read10X(data.dir = "./OriginalReferenceFilteredMatrix/Night2/")
Pineal2_Night2 <- CreateSeuratObject(Pineal2_Night2.matrix, project = "Pineal2_Night2", min.cells = 2, min.genes = 800)
```

```{r}
print(paste(dim(Pineal2_Night2.matrix)[2] - dim(Pineal2_Night2@raw.data)[2], " cells were filtered from the original matrix.", sep=''))
```

Calculate percent expression of mitochondrial genes, output QC plots. 
```{r QC stats}
Pineal2_Night2 <- MetadataInit(Pineal2_Night2, ID.prefix = "Night2")
Pineal2_Night2.mito.genes <- grep("^Mt-", rownames(Pineal2_Night2@data), value = T)
Pineal2_Night2.percent.mito <- Matrix::colSums(Pineal2_Night2@raw.data[Pineal2_Night2.mito.genes, ])/Matrix::colSums(Pineal2_Night2@raw.data)
Pineal2_Night2 <- AddMetaData(Pineal2_Night2, Pineal2_Night2.percent.mito, "percent.mito")
GenePlot(Pineal2_Night2, "nUMI","nGene")
VlnPlot(Pineal2_Night2, c("nUMI","nGene","percent.mito"),nCol=3, group.by = "orig.ident")
```

Filter cells, cutoffs based on QC plots. 
```{r Filter by nGene/nUMI, results="hold"}
GenePlot(Pineal2_Night2, "nUMI", "nGene")
Pineal2_Night2 <- FilterCells(Pineal2_Night2, subset.names = "nUMI", high.thresholds = 28000)
GenePlot(Pineal2_Night2, "nUMI","nGene")
VlnPlot(Pineal2_Night2, c("nUMI","nGene","percent.mito"),nCol=3)
```

```{r Log Normalize}
Pineal2_Night2 <- NormalizeData(Pineal2_Night2, scale.factor = 1e4, display.progress = F)
```

```{r Find Variable Genes, echo=TRUE}
Pineal2_Night2 <- FindVariableGenes(Pineal2_Night2, x.low.cutoff = 0.0125, x.high.cutoff = 3, y.cutoff = 0.3, do.plot = F)
print(paste(length(Pineal2_Night2@var.genes), " variable genes selected.", sep=""))
```

```{r Scale/Regress, echo=TRUE}
Pineal2_Night2 <- ScaleData(Pineal2_Night2, display.progress = F)
```

```{r PCA I, echo=TRUE, message=FALSE, warning=FALSE}
Pineal2_Night2 <- RunPCA(Pineal2_Night2, pc.genes = Pineal2_Night2@var.genes, pcs.compute = 40, do.print = F)
Pineal2_Night2 <- ProjectPCA(Pineal2_Night2, do.print = F)
```
```{r PCA Plot I, echo=TRUE, message=FALSE, warning=FALSE}
PCAPlot(Pineal2_Night2, no.legend = T)
PCElbowPlot(Pineal2_Night2, num.pc = 40)
PCHeatmap(Pineal2_Night2, pc.use = 1:6, cells.use = 200, num.genes = 25, do.balanced = F)
PCHeatmap(Pineal2_Night2, pc.use = 7:12, cells.use = 150, num.genes = 25, do.balanced = T)
PCHeatmap(Pineal2_Night1, pc.use = 13:18, cells.use = 150, num.genes = 25, do.balanced = T)
```

PCs selected for generating TSNE plot. Number of PCs and resolution parameters will be refined after combining samples.
```{r Clustering, echo=TRUE, message=FALSE, warning=FALSE}
Pineal2_Night2 <- FindClusters(Pineal2_Night2, dims.use = 1:20, reduction.type = "pca", resolution = 1.5, print.output = F, save.SNN = T)
```

```{r Generate TSNE, echo=TRUE, message=FALSE, warning=FALSE}
Pineal2_Night2 <- RunTSNE(Pineal2_Night2, dims.use = 1:20, do.fast = T)
```

```{r Plot TSNE, echo=TRUE, results="hide"}
Pineal2_Night2 <- BuildClusterTree(Pineal2_Night2, genes.use = Pineal2_Night2@var.genes, do.plot = T, do.reorder = T, reorder.numeric = T)
TSNEPlot(Pineal2_Night2, do.label = T, do.return = T) + ggtitle("PCs 1-20, 1.5 res")
FeaturePlot(Pineal2_Night2, "nUMI", cols.use = c("light grey","red"))
FeaturePlot(Pineal2_Night2, "nGene", cols.use = c("light grey","red"))
```

```{r Markers}
FeaturePlot(Pineal2_Night2, c("Tph1","Asmt","Esm1","Apoe","Penk","Lum","Vwf","Sparcl1","Lyz2","C1qa","RT1-Bb"), cols.use=c("light grey","red"))
DotPlot(object = Pineal2_Night2, genes.plot = c("Tph1","Asmt","Esm1","Apoe","Penk","Lum","Vwf","Sparcl1","Lyz2","C1qa","RT1-Bb"))
```

```{r}
sessionInfo()
```